Which ``Bad Smells'' Can Be Ignored?

### 2016-03-12 tex/prediction_stats.tex
final save for the fse submission

	\caption{Training and test {\em data set properties} for  Jureczko data ,
		sorted by \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is usable if it has a recall of 60\% or more and false alarm of 30\% or less (and note that, after tuning, there are more usable data sets than before). Results  	\colorbox{celadon}{ marked with ``$\star$''} show large improvements in performance, after tuning
		(lower {\em pf} or higher {\em pd}).
		Data in  the  \colorbox{lavenderpink}{three bottom rows}, marked with ``$\times$'', are  performing
		poorly-- that data so few non-defective examples  that it  is hard for
		our learners to distinguish between classes.
	}\label{fig:j}
\end{figure*}

>>>>

	\caption{Training and test {\em data set properties} for  Jureczko data ,
		sorted by \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is usable if it has a recall of 60\% or more and false alarm of 30\% or less (and note that, after tuning, there are more usable data sets than before). Results  	\colorbox{celadon}{ marked with ``$\star$''} show large improvements in performance, after tuning
		(lower {\em pf} or higher {\em pd}).
		Data in  the  \colorbox{lavenderpink}{three bottom rows}, marked with ``$\times$'', are  performing
		poorly-- that data so many defective examples  that it  is hard for
		our learners to distinguish between classes.
	}\label{fig:j}
\end{figure*}

### 2016-03-12 tex/refactor.tex
final save for the fse submission

\begin{figure}[!t] 
\scriptsize
\centering
\begin{tabular}{r|c|c|c|c|c}

\begin{turn}{75}Fowler'99~\cite{fowler99}, and~\cite{Kerievsky2005})\end{turn} &\begin{turn}{75} Lanza'06~\cite{Lanza2006}\end{turn} & \begin{turn}{75}SonarQube~\cite{sq15} \end{turn} &  \begin{turn}{75}Yamashita'13\cite{Yamashita2013} \end{turn}& \begin{turn}{75}Atwood'06\cite{Atwood06}\end{turn}  & \begin{turn}{75} Developer Survey 2015\end{turn}\\\hline
  Alt. Classes with Diff. Interfaces & & & & \checkmark & \\
  Combinatorial Explosion~\cite{Kerievsky2005} & & & & \checkmark & \\
  Comments & & & 11 & \checkmark & VL\\
  Conditional Complexity~\cite{Kerievsky2005} & & & 14 & \checkmark & ?\\
  Data Class & \checkmark & & & \checkmark &\\
  Data Clumps &  &  & & \checkmark &\\
  Divergent Change & & & & \checkmark & \\
  Duplicated Code & \checkmark & \checkmark & 1 & \checkmark & VH\\
  Feature Envy & \checkmark & & 8 & \checkmark &\\

  Inappropriate Intimacy & & \checkmark & & \checkmark & L\\
  Indecent Exposure~\cite{Kerievsky2005} & & & & \checkmark & ?\\
  Incomplete Library Class & & & & \checkmark &\\
  Large Class & \checkmark & \checkmark & 4 & \checkmark & VH\\
  Lazy Class/Freeloader & & \checkmark & 7 & \checkmark &\\
  Long Method & \checkmark& \checkmark & 2 & \checkmark & VH\\
  Long Parameter List &  & \checkmark & 9 & \checkmark & L \\

  Message Chains & & & & \checkmark & H\\
  Middle Man & &  & & \checkmark &\\
  Oddball Solution~\cite{Kerievsky2005} & & & & \checkmark & \\
  Parallel Inheritance Hierarchies & & & & \checkmark &\\
  Primitive Obsession &  & & & \checkmark &\\

  Refused Bequest & \checkmark & \checkmark & & \checkmark & \\ 
  Shotgun Surgery & \checkmark& & & \checkmark & \\
  Solution Sprawl~\cite{Kerievsky2005} & & & & \checkmark &\\
  Speculative Generality & & & & \checkmark & L\\
  Switch Statements &  & \checkmark & & & L\\
  Temporary Field & & \checkmark & & \checkmark & ?\\
  \end{tabular}
%   \multicolumn{5}{l}{} \\
%   \multicolumn{5}{l}{\textsuperscript{\textdagger} + Exact rule, - Possibly related rule} \\
%     \multicolumn{5}{l}{\textsuperscript{\textdaggerdbl} + is included in list} \\
%     \multicolumn{5}{l}{\textsuperscript{\textexclamdown} VH: Very High, H: High, L: Low, VL: Very Low, ?: Still investigating} \\
%   \multicolumn{5}{l}{\textsuperscript{*} Computation is based on more than simple metrics.} \\

\caption{Bad   smells from different sources.  Check marks (\checkmark) denote   a bad smell was mentioned.
Numbers or symbolic labels (e.g. "VH") denote  a priorization comment (and
``?'' indicates lack of consensus). Empty cells
denote some bad smell listed in column one that was not found relevant
in other studies.
Note:    there are many blank cells.}
\label{fig:smells}
\end{figure}

>>>>

\begin{figure}[!t] 
\scriptsize
\centering
\begin{tabular}{r|c|c|c|c}

\begin{turn}{75}Fowler'99~\cite{fowler99} and~\cite{Kerievsky2005}\end{turn} &\begin{turn}{75} Lanza'06~\cite{Lanza2006}\end{turn} & \begin{turn}{75}SonarQube~\cite{sq15} \end{turn} &  \begin{turn}{75}Yamashita'13\cite{Yamashita2013} \end{turn}& \begin{turn}{75} Developer Survey 2015\end{turn}\\\hline
  Alt. Classes with Diff. Interfaces & & & & \\
  Combinatorial Explosion~\cite{Kerievsky2005} & & &  & \\
  Comments & & & 11 & VL\\
  Conditional Complexity~\cite{Kerievsky2005} & & & 14  & ?\\
  Data Class & \checkmark & &  &\\
  Data Clumps &  &  &  &\\
  Divergent Change & & &  & \\
  Duplicated Code & \checkmark & \checkmark & 1  & VH\\
  Feature Envy & \checkmark & & 8  &\\

  Inappropriate Intimacy & & \checkmark &  & L\\
  Indecent Exposure~\cite{Kerievsky2005} & & &  & ?\\
  Incomplete Library Class & & &  &\\
  Large Class & \checkmark & \checkmark & 4  & VH\\
  Lazy Class/Freeloader & & \checkmark & 7  &\\
  Long Method & \checkmark& \checkmark & 2  & VH\\
  Long Parameter List &  & \checkmark & 9  & L \\

  Message Chains & & &  & H\\
  Middle Man & &  &  &\\
  Oddball Solution~\cite{Kerievsky2005} & & &  & \\
  Parallel Inheritance Hierarchies & & &  &\\
  Primitive Obsession &  & &  &\\

  Refused Bequest & \checkmark & \checkmark &  & \\ 
  Shotgun Surgery & \checkmark& &  & \\
  Solution Sprawl~\cite{Kerievsky2005} & & &  &\\
  Speculative Generality & & &  & L\\
  Switch Statements &  & &  & L\\
  Temporary Field & & \checkmark &  & ?\\
  \end{tabular}
%   \multicolumn{5}{l}{} \\
%   \multicolumn{5}{l}{\textsuperscript{\textdagger} + Exact rule, - Possibly related rule} \\
%     \multicolumn{5}{l}{\textsuperscript{\textdaggerdbl} + is included in list} \\
%     \multicolumn{5}{l}{\textsuperscript{\textexclamdown} VH: Very High, H: High, L: Low, VL: Very Low, ?: Still investigating} \\
%   \multicolumn{5}{l}{\textsuperscript{*} Computation is based on more than simple metrics.} \\

\caption{Bad   smells from different sources.  Check marks (\checkmark) denote   a bad smell was mentioned.
Numbers or symbolic labels (e.g. "VH") denote  a priorization comment (and
``?'' indicates lack of consensus). Empty cells
denote some bad smell listed in column one that was not found relevant
in other studies.
Note:\   there are many blank cells.}
\label{fig:smells}
\end{figure}
